Follow-up Samples

### 2017-03-07 submission/manuscript_outline_20161024.Rmd
make sure new paths all work

---
title: ''
csl: microbiome.csl
fontsize: 12pt
output:
  word_document: default
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: reference.bib
---

@@

```{r rdata_tables}
# Extra data and meta data needed
good_metaf <- read.csv('../results/tables/mod_metadata/good_metaf_final.csv', header = T, stringsAsFactors = F)
metaI <- read.csv('../results/tables/mod_metadata/metaI_final.csv', header = T, stringsAsFactors = F)
total_sub_Seqs <- read.delim('../data/process/final.0.03.subsample.shared', header = T) %>% 
  select(contains("Otu0")) %>% rowSums()

# initial microbiome and FIT description data 
change_summary <- read.csv('../results/tables/change_theta_fit_summary.csv', header = T, row.names = 1)
alpha_summary <- read.csv('../results/tables/alpha_table_summary.csv', header = T, row.names = 1)
beta_summary <- read.csv('../results/tables/beta_diver_summary.csv', header = T, row.names = 1)
time_pvalues <- read.csv("../results/tables/time_pvalues.csv", header = T, row.names = 1)
time_summary <- read.csv("../results/tables/time_summary_data.csv", header = T, row.names = 1)
all_OTU_pair_wilcox <- read.csv("../results/tables/OTU_paired_wilcoxson_test.csv", header = T)

# Main CRC bacteria differences between Adenoma and Carcinoma
main_crc_bugs_summary <- read.csv('../results/tables/adn_crc_maybe_pvalue_summary.csv', header = T, row.names = 1)
crc_bug_info <- read.csv("../results/tables/adn_crc_maybe_diff.csv", header = T, stringsAsFactors = F)

# Lesion Model 
lesion_top10_varsMDA <- read.csv('../results/tables/reduced_lesion_model_top_vars_MDA_Summary.csv', header = T)
lesion_imp_vars <- read.csv('../results/tables/rf_otu_tax.csv', header = T, row.names = 1)
lesion_AUC_run_summary <- read.csv('../results/tables/Reduced_ROC_model_summary.csv', header = T)

# IF Model
IF_top10_varsMDA <- read.csv('../results/tables/reduced_IF_model_top_vars_MDA_Summary.csv', header = T)
IF_imp_vars <- read.csv('../results/tables/if_rf_otu_tax.csv', header = T, row.names = 1)
IF_AUC_run_summary <- read.csv('../results/tables/reduced_IF_ROC_model_summary.csv', header = T)

# All model information
all_probs_paired_wilcox <- read.csv('../results/tables/all_models_wilcox_paired_pvalue_summary.csv', header = T, stringsAsFactors = F)
all_pred_stat_summary <- read.csv('../results/tables/all_models_summary_info.csv', header = T, stringsAsFactors = F)
all_confu_matrix <- read.csv('../results/tables/all_models_confusion_summary.csv', header = T, stringsAsFactors = F)

# Common Variable Info
common_vars_summary <- read.csv('../results/tables/pvalue_IF_lesion_common_imp_vars.csv', header = T, row.names = 1, stringsAsFactors = F)

#Therapy Info
chemo_rad_summary <- read.csv('../results/tables/probs_chemo_rad_pvalue_summary.csv', header = T, row.names = 1)

>>>>

---
title: ''
csl: microbiome.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: reference.bib
---

@@

```{r rdata_tables}
# Extra data and meta data needed
good_metaf <- read.csv('../data/process/mod_metadata/good_metaf_final.csv', header = T, stringsAsFactors = F)
metaI <- read.csv('../data/process/mod_metadata/metaI_final.csv', header = T, stringsAsFactors = F)
total_sub_Seqs <- read.delim('../data/process/final.0.03.subsample.shared', header = T) %>% 
  select(contains("Otu0")) %>% rowSums()

# initial microbiome and FIT description data 
change_summary <- read.csv('../data/process/tables/change_theta_fit_summary.csv', header = T, row.names = 1)
alpha_summary <- read.csv('../data/process/tables/alpha_table_summary.csv', header = T, row.names = 1)
beta_summary <- read.csv('../data/process/tables/beta_diver_summary.csv', header = T, row.names = 1)
time_pvalues <- read.csv("../data/process/tables/time_pvalues.csv", header = T, row.names = 1)
time_summary <- read.csv("../data/process/tables/time_summary_data.csv", header = T, row.names = 1)
all_OTU_pair_wilcox <- read.csv("../data/process/tables/OTU_paired_wilcoxson_test.csv", header = T)

# Main CRC bacteria differences between Adenoma and Carcinoma
main_crc_bugs_summary <- read.csv('../data/process/tables/adn_crc_maybe_pvalue_summary.csv', header = T, row.names = 1)
crc_bug_info <- read.csv("../data/process/tables/adn_crc_maybe_diff.csv", header = T, stringsAsFactors = F)

# Lesion Model 
lesion_top10_varsMDA <- read.csv('../data/process/tables/reduced_lesion_model_top_vars_MDA_Summary.csv', header = T)
lesion_imp_vars <- read.csv('../data/process/tables/rf_otu_tax.csv', header = T, row.names = 1)
lesion_AUC_run_summary <- read.csv('../data/process/tables/Reduced_ROC_model_summary.csv', header = T)

# IF Model
IF_top10_varsMDA <- read.csv('../data/process/tables/reduced_IF_model_top_vars_MDA_Summary.csv', header = T)
IF_imp_vars <- read.csv('../data/process/tables/if_rf_otu_tax.csv', header = T, row.names = 1)
IF_AUC_run_summary <- read.csv('../data/process/tables/reduced_IF_ROC_model_summary.csv', header = T)

# All model information
all_probs_paired_wilcox <- read.csv('../data/process/tables/all_models_wilcox_paired_pvalue_summary.csv', header = T, stringsAsFactors = F)
all_pred_stat_summary <- read.csv('../data/process/tables/all_models_summary_info.csv', header = T, stringsAsFactors = F)
all_confu_matrix <- read.csv('../data/process/tables/all_models_confusion_summary.csv', header = T, stringsAsFactors = F)

# Common Variable Info
common_vars_summary <- read.csv('../data/process/tables/pvalue_IF_lesion_common_imp_vars.csv', header = T, row.names = 1, stringsAsFactors = F)

#Therapy Info
chemo_rad_summary <- read.csv('../data/process/tables/probs_chemo_rad_pvalue_summary.csv', header = T, row.names = 1)
